INTELLIGENT SYSTEMS

### 2021-03-18 paper_2.tex
fix Corollary

\subsection{LSC SUPERPIXEL}
The task of LSC is to discover the relationships that exist between the objective 
functions ($ F_{N_{cuts}} $) (\ref{FNcuts}), of the normalized cuts, and the objective functions 
of the weighted K-means ($ F_{km}$) (\ref{Fkm}). 
\begin{equation} \label{Fkm}
    F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 
\end{equation}
\begin{equation} \label{Centroid}
    m_k = \frac{\sum_{q\in\pi_k}\omega(q)\phi(q)}{\sum_{q\in\pi_k}\omega(q)}
\end{equation}
\begin{equation} \label{FNcuts}
    F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)}
\end{equation}
Where $ m_k $ (\ref{Centroid}) represent the average point, or centroid, of each cluster. Within 
the formulation of normalized cuts, each data Point corresponds to a node 
within a graph \emph{G = (V, E, W)} where \emph{V} is the set of all nodes, \emph{E} represents 
the set of all edges connected and \emph{W} represents the result returned by a 
similarity function between nodes. The criterion of normalized cuts is based 
on maximizing the $ F_{N_{cuts}} $ function. The minimization or maximization problems 
are called \emph{optimization problems} which can be solved by using a positive kernel of 
a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary 1}:

\begin{corollary} 
    Optimizations of the objective functions of the weighted K-means
    and the normalized cuts are mathematically equivalent if (\ref{eq4}) and (\ref{eq5}) 
    hold simultaneously. The symbol $ \cdot $ stands for inner product.
\end{corollary}

>>>>

\subsection{LSC SUPERPIXEL}
The task of LSC is to discover the relationships that exist between the objective 
functions ($ F_{N_{cuts}} $) (\ref{FNcuts}), of the normalized cuts, and the objective functions 
of the weighted K-means ($ F_{km}$) (\ref{Fkm}). 
\begin{equation} \label{Fkm}
    F_{km} = \sum_{k=1}^K\sum_{p\in\pi_k}\omega(p)= || \phi(p)-m_k ||^2 
\end{equation}
\begin{equation} \label{Centroid}
    m_k = \frac{\sum_{q\in\pi_k}\omega(q)\phi(q)}{\sum_{q\in\pi_k}\omega(q)}
\end{equation}
\begin{equation} \label{FNcuts}
    F_{N_{cuts}} = \frac{1}{K}\sum_{k=1}^K\frac{\sum_{p\in\pi_k}\sum_{q\in\pi_k}W(p,q)}{\sum_{p\in\pi_k}\sum_{q\in{V}}W(p,q)}
\end{equation}
Where $ m_k $ (\ref{Centroid}) represent the average point, or centroid, of each cluster. Within 
the formulation of normalized cuts, each data Point corresponds to a node 
within a graph \emph{G = (V, E, W)} where \emph{V} is the set of all nodes, \emph{E} represents 
the set of all edges connected and \emph{W} represents the result returned by a 
similarity function between nodes. The criterion of normalized cuts is based 
on maximizing the $ F_{N_{cuts}} $ function. The minimization or maximization problems 
are called \emph{optimization problems} which can be solved by using a positive kernel of 
a matrix. To see the relationship between the two functions, the Dhillon's concept \cite{0781426526} is extended, to obtain {\bfseries Corollary \ref{Corollary1}}:

\begin{corollary} \label{Corollary1}
    Optimizations of the objective functions of the weighted K-means
    and the normalized cuts are mathematically equivalent if (\ref{eq4}) and (\ref{eq5}) 
    hold simultaneously. The symbol $ \cdot $ stands for inner product.
\end{corollary}
